%List of own publications listed here:
%=========================================
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Publications}
\pagestyle{plain}
\vfill
\begin{center}{\huge{\textbf{List of Publications}} \par}\end{center}
\vfill
The following publications have been published while in conduct of this study:
\vspace{20pt}
\begin{itemize} 

\item Abdelrahman M. Hassan, Catherine M. Elias, Omar M. Shehata, and Elsayed I. Morgan.  A Global Integrated Artificial Potential Field/Virtual Obstacles Path Planning Algorithm for Multi-Robot System Applications. In \textit{International Research Journal of Engineering and Technology (IRJET)} 4.9 (2017): 1198-1204.

\item Abdelrahman F. ElAshry, Mohamed M. Ramadan, Ziad A. Alalaily, Mahmoud M. Zaied, Catherine M. Elias, Omar M. Shehata, and Elsayed I. Morgan. Group Formation Control Algorithm for a Team of Autonomous Mobile Robots. In \textit{The International Journal of Robotics Research} Under Review (2017).

\item Catherine M. Elias, Shaimaa K. El-Baklish, Nada N. El-Ghandoor, Omar M. Shehata, and Elsayed I. Morgan. Practical Hybrid Graph-Based Formation Control Algorithm for Leader-Follower Trajectory Tracking Problem. In \textit{IEEE transactions on Robotics and Automation}, Under Review (2017).

\item Ahmed H. Salem, Catherine M. Elias, Omar M. Shehata, and Elsayed I. Morgan. A Two-Stage Voronoi-Based Deployment Algorithm with obstacle Avoidance for 2-D Continuously Expanding Area Coverage Control Problem. In \textit{International Journal of Intelligent Systems}, Under Review (2017).

\item Amr K. Gouda, Catherine M. Elias, Omar M. Shehata, and Elsayed I. Morgan. A Hybrid Agent-based Controller integrating Flocking and Virtual Leader-Follower Approaches for Group Formation Problems. \textit{Robotics and autonomous systems}, Under Review (2017).


\end{itemize}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage

%[\tiny{$\blacksquare$}]